CLT Results

### 2022-04-03 analysis/clt_irt_analysis.Rmd
order DIF

```{r}
irt3_dif <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ sex |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ sex |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

saveRDS(irt3_dif, "../saves/irt3_dif.rds")
```

```{r}
coef_irt3_dif <- coef(irt3_dif)

eta <- bind_rows(
  coef_irt3_dif$targetWord[, , "eta_sexf"] %>%
	as_tibble(rownames = "item")%>%mutate(sex = "female"),
  coef_irt3_dif$targetWord[, , "eta_sexm"] %>%
	as_tibble(rownames = "item")%>%mutate(sex = "male")
  )%>%mutate(nlpar = "Easiness")

alpha <- 
  bind_rows(
    coef_irt3_dif$targetWord[, , "logalpha_sexf"] %>%
	exp() %>%
	as_tibble(rownames = "item")%>%mutate(sex = "female"),
	    coef_irt3_dif$targetWord[, , "logalpha_sexm"] %>%
	exp() %>%
	as_tibble(rownames = "item")%>%mutate(sex = "male")
  )%>%mutate(nlpar = "Discrimination")

params <- bind_rows(eta, alpha) %>%
	select(-Est.Error) %>%
  left_join(aoa%>%rename(item = targetWord))

ggplot(params,aes(reorder(item, -aoa_german_comb), Estimate, ymin = Q2.5, ymax = Q97.5)) +
	facet_wrap("nlpar", scales = "free_x") +
	geom_pointrange(aes(col = sex), position = position_dodge(width = .5)) +
	coord_flip() +
  scale_color_colorblind()+
	labs(x = "Item")+
  theme_minimal()
```

@@

```{r}
irt3_dif <- add_criterion(irt3_dif, "loo")

loo_compare(irt3, irt3_dif)%>%as_tibble(rownames = "model")
```

@@

firt_1F <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 5000))
firt_2F <- mirt(firt_dat, 2, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 5000))

>>>>

@@

### Sex

```{r}
irt3_dif_sex <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ sex  |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ sex  |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

saveRDS(irt3_dif_sex, "../saves/irt3_dif_sex.rds")
```

```{r}
irt3_dif_sex <- add_criterion(irt3_dif_sex, "loo")

loo_compare(irt3, irt3_dif_sex)%>%as_tibble(rownames = "model")
```

```{r}
coef_irt3_dif_sex <- coef(irt3_dif_sex)

eta_sex <- bind_rows(
  coef_irt3_dif_sex$targetWord[, , "eta_sexf"] %>%
	as_tibble(rownames = "item")%>%mutate(sex = "female"),
  coef_irt3_dif_sex$targetWord[, , "eta_sexm"] %>%
	as_tibble(rownames = "item")%>%mutate(sex = "male")
  )%>%mutate(nlpar = "Easiness")

alpha_sex <- 
  bind_rows(
    coef_irt3_dif_sex$targetWord[, , "logalpha_sexf"] %>%
	exp() %>%
	as_tibble(rownames = "item")%>%mutate(sex = "female"),
	    coef_irt3_dif_sex$targetWord[, , "logalpha_sexm"] %>%
	exp() %>%
	as_tibble(rownames = "item")%>%mutate(sex = "male")
  )%>%mutate(nlpar = "Discrimination")

params_sex <- bind_rows(eta_sex, alpha_sex) %>%
	select(-Est.Error) %>%
  left_join(aoa%>%rename(item = targetWord))

ggplot(params_sex,aes(reorder(item, -aoa_german_comb), Estimate, ymin = Q2.5, ymax = Q97.5)) +
	facet_wrap("nlpar", scales = "free_x") +
	geom_pointrange(aes(col = sex), position = position_dodge(width = .5)) +
	coord_flip() +
  scale_color_colorblind()+
	labs(x = "Item")+
  theme_minimal()
```

### Order

```{r}
irt3_dif_order <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ order  |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ order  |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

saveRDS(irt3_dif_order, "../saves/irt3_dif_order.rds")
```

```{r}
irt3_dif_order <- add_criterion(irt3_dif_order, "loo")

loo_compare(irt3, irt3_dif_order)%>%as_tibble(rownames = "model")
```

```{r}
coef_irt3_dif_order <- coef(irt3_dif_order)

eta_order <- bind_rows(
  coef_irt3_dif_order$targetWord[, , "eta_orderorderA"] %>%
	as_tibble(rownames = "item")%>%mutate(order = "A"),
  coef_irt3_dif_order$targetWord[, , "eta_orderorderB"] %>%
	as_tibble(rownames = "item")%>%mutate(order = "B")
  )%>%mutate(nlpar = "Easiness")

alpha_order <- 
  bind_rows(
    coef_irt3_dif_order$targetWord[, , "logalpha_orderorderA"] %>%
      exp() %>%
      as_tibble(rownames = "item")%>%mutate(order = "A"),
    coef_irt3_dif_order$targetWord[, , "logalpha_orderorderB"] %>%
      exp() %>%
      as_tibble(rownames = "item")%>%mutate(order = "B")
  )%>%mutate(nlpar = "Discrimination")

params_order <- bind_rows(eta_order, alpha_order) %>%
	select(-Est.Error) %>%
  left_join(aoa%>%rename(item = targetWord))

ggplot(params_order,aes(reorder(item, -aoa_german_comb), Estimate, ymin = Q2.5, ymax = Q97.5)) +
	facet_wrap("nlpar", scales = "free_x") +
	geom_pointrange(aes(col = order), position = position_dodge(width = .5)) +
	coord_flip() +
  scale_color_colorblind()+
	labs(x = "Item")+
  theme_minimal()
```

@@

firt_1F <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000))
firt_2F <- mirt(firt_dat, 2, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000))
